---
title: "bootstrap"
author: "Ayeshra Acharya"
date: "11/24/2020"
output: github_document
---

## Bootstrapping 
- Repeated sampling is important if you want to know something about population. Repeated sampling doesn't happen in reality. Repeated sampling CAN happen on a computer. O.o 

- Bootstrapping: something you do over and over. Critical in modern statistics. Basic idea: use data that you have, treat as population and draw samples from that. 
- Draw a bootstrap sample from the sample you have 
- The bootstrap sample has same size as og. 
With replacement 
Draw sample form sample, variablity with replacement should mimic what happens in population. 
- Some ppl are drawn 2x, some 0. 
- Repeated sampling works! 
## Revisit nyc airbnb


```{r}
data("nyc_airbnb")
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```


```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point()
```

```{r}
airbnb_boot_results = 
  nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  drop_na(stars) %>% 
  bootstrap(1000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(price ~ stars, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) 
airbnb_boot_results %>% 
  group_by(term) %>% 
  summarize(
    mean_est = mean(estimate),
    sd_est = sd(estimate)
  )
```

Compare this to `lm`

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  drop_na(stars) %>% 
  lm(price ~ stars, data = .) %>% 
  broom::tidy()
```

```{r}
airbnb_boot_results %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + 
  geom_density()
```