---
title: "crossvalidation_nepaldata"
author: "Ayeshra Acharya"
date: "11/24/2020"
output: github_document
---
Nepali children growth. CV. 

```{r}
child_growth_df = 
  read_csv("./data/nepalese_children.csv") %>%
  mutate(
    weight_cp = (weight>7)* (weight - 7)
  )
```
First, let's look at how well weight predicts arm circum? 
```{r}
child_growth_df %>%
  ggplot(aes(x=weight,y=armc)) +
  geom_point(alpha=0.3)
```
higher weight = higher armc at quick glance. 
Maybe there is a line? 

So we have to compare 3 models
- Linear
- One piece straight, allow change and then straight again 
- Smooth curve 
OK SO in the below problem, we are looking at how well weight predicts arm circum. 
the predictor is weight. after ~
```{r}
linear_mod = lm(armc ~ weight, data = child_growth_df)
pwlin_mod = lm(armc ~ weight + weight_cp, data = child_growth_df)
smooth_mod = gam(armc ~ s(weight), data = child_growth_df)
```

Ok now let's fit the models we care about. 

If we look at the 3 models, the linear model is straight line, pw lin model curves a little and then smooth model is a bit more squiggly. 
-- Which is right one to use?

CROSS VALIDATION PROCEDURE. 
"Try to understand model fit using CV" 

DO RMSE, violin plot of RMSEs. 
This one is a lot closer than other one. We have to pick which model is best without really looking at p values. 
LINEAR model does ok. PW does better, smooth does a little better.

Which one to choose? PW lin model probably. 
- Because there is a clear improvement from linear to PW. BUT it is not huge improvement from PW to smooth model. Interpreation for PW lin is more stragiht forward than smoot model. 
- Smooth model is more correct but harder to interpret. 
- Choice is not always super direct. Nuances exist. Tradeoffs exist. 
