---
title: "linear_models"
author: "Ayeshra Acharya"
date: "11/23/2020"
output: html_document
---

Lm is linear models, glm for generalized lnear models
Arguments include: formula, data
Output is complex and kind of messy, use broom package!
- Use broom after running LM 

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(1)
```
```{r}
data("nyc_airbnb")
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

## Fit a model. We want to know what is the price of an an airbnb rental and how is it related to star (numeric predictor) and borough(categorical predictor). Fir some line that runs through stars and maybe different for each borough. 
```{r}
nyc_airbnb %>%
  ggplot(aes(x = stars,y=price,color=borough)) + 
  geom_point()
```
Let's fit the model we care about. Linear model relating price to starts to borough. 
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Let's look at the result.. If you look at the summary you get way more, R squared, residuals etc. You can also get coefficients of the fit. There has been useful stuff that R has produced using "fit", but it is not great. So we will use broom! 

```{r}
broom::glance(fit)
```
Here, we get the r-squared, we get p-value etc. This is some of the most relevant info. Global test p-value. 

However, this below might be better. 
```{r}
broom::tidy(fit)
``` 
This above is showing us: intercept, coefficient for stars, brooklyn to reference group, manhattan to reference group and queens to reference group. 
How to interpret: One unit increase in stars, I expect the price to go up 32 dollars, keeping the borough fixed.
Brooklyn room airbnb is 40 dollars more expensive than Bronx. Manhattan is 90 dollars more expensive, Queens is 13 dollars more expensive. 
We can see p value and assess significance. 
- Remember, this is a data frame. If we aren't interested in certain things, 
we can omit. For example:
```{r}
broom::tidy(fit) %>%
  select(-std.error,-statistic) %>%
  mutate(
    term = str_replace(term,"borough","Borough:")
  ) %>%
  knitr::kable()
``` 
## Be in control of factors.
For example, borough is a character variable. Very often, this gets converted into a factor variable. You perserve text, but add another string... Idk but basically, Bronx is being used as the reference here. 
- But what if, I want to make reference category the most common one? SO, I want reference group to be the one that has the most airbnb rentals. I want room type to be treated as factor variable, not alphabetical but most common .
Mutate so that borough is factor and we are putting it in order of frequency of borough. 

```{r}
nyc_airbnb = 
  nyc_airbnb %>%
  mutate(
    borough = fct_infreq(borough), 
    room_type = fct_infreq(room_type)
  )
```

Now, let's look at the plot again. 
```{r}
nyc_airbnb %>%
  ggplot(aes(x=stars,y=price, color=borough)) +
  geom_point()
``` 
It is very similar, but the ordering on axis has changed. Borough is in order of frequency of these things. 

## Re fit the model 
```{r}

fit = lm(price ~ stars + borough, data = nyc_airbnb)
broom::tidy(fit)

``` 

The difference now is that manhattan became the reference group and everythig else is being compared to it. We didn't change model in a fundamental way, we changed the reference group. 

## Diagnostics 
```{r}
residuals(fit)
```
Up until now we have been using the above approach. We get super long vector. we want to get all variables and then tack onto that fitted variables that go along with it. So we will take advantage of modelr package. 
```{r}
modelr::add_residuals(nyc_airbnb,fit)
``` 
This dataset has a column for residual value. Residuals based on model fit. We can look at distributions of residuals, for instance. 
```{r}
nyc_airbnb %>%
  modelr::add_residuals(fit) %>%
  ggplot(aes(x=borough,y=resid)) + 
  geom_violin() + 
  ylim(-500,1500)

nyc_airbnb %>%
  modelr::add_residuals(fit) %>%
  ggplot(aes(x=stars,y=resid)) +
  geom_point() + 
  facet_wrap(.~ borough)
``` 
What is this telling us?? 
In Manhattan, as we get to higher star values, residuals get wider distributions. 4 5 stars in Manhattan, distribution of residuals in Manhattan gets higher. Same in Brooklyn. 
Why does Queens have one outlier?? 
Bronx doesn't have this issue 

## Hypothesis Tests
```{r}
fit %>%
  broom::tidy()
``` 
If we have categorical predictor, we want to know if categorical predictor as a whole is significant in my model. 

What about the significance of borough? we can do f test or ANOVA. adding borough into one model to compare 
```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null,fit_alt)
broom::tidy()
``` 

## Nest data, fit models 
Is there an association between price and stars? Does this association differ by borough? 
- We want different lines for each borough?
- Can also study across room type. 
- We can fit interaction terms! 
Interactions are important, and complicated. 

```{r}
fit = lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)
broom::tidy(fit)
``` 
First row: overall, stars has this effect. 
Then, we get it for each as we go down the rows. 
Looks like stars increasing does make a difference. 

If you wanted to assess statistical sig, you can compare 1 fit that has itneraction and another that doesn't and ask if that's an improvement in model. Is it important contributor? 

This is more exploratory but maybe easier to understand. What is the effect of sstars in Manhattan, stars in BK, stars in Bronx? 
Build up from scratch a bit. 
Results columns maps across columns. 
In this we are fitting a model to each borough. Broom tidying is tidying all. 
```{r}
nyc_airbnb %>%
  nest(data = -borough) %>%
  mutate(
    models = map(.x = data, ~lm(price ~ stars, data = .x)),
    results = map(models,broom::tidy)
  ) %>%
  select(-data,-models) %>%
  unnest(results)
``` 
As we can see from above, in Manhattan, there is a sig association between stars and price. 1 unit increase in stars = 43 dollar increase.
In Bronx theres hardly any association between stars and price. 
We can't say anything about whether models are different than each other bc we didn't fit this all in a join model. This is more exploratory. 



Below, we are looking at what is the effect of stars on bronx, queens, bk, manhattan? What is the effect of room type on each of these? Going from an entire apartment to private room will... 
We are getting an idea of what's going on. 

```{r}
nyc_airbnb %>%
  nest(data = -borough) %>%
  mutate(
    models = map(.x = data, ~lm(price ~ stars, data = .x)),
    results = map(models,broom::tidy)
  ) %>%
  select(-data,-models) %>%
  unnest(results) %>%
  filter(term != "(Intercept)") %>%
  select(borough,term,estimate) %>%
  pivot_wider(
    names_from = borough, 
    values_from = estimate
  )
``` 

Let's nest even more. What if we wanted to look at neighborhoods within Manhattan? Getting a separate model for each of the 32 neighborhoods in Manhattan.
```{r}
nyc_airbnb %>%
  filter(borough == "Manhattan") %>%
  nest(data = -neighborhood) %>%
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models,broom::tidy)
  ) %>%
  select(-data,-models) %>%
  unnest(results) %>%
  filter(str_detect(term,"room_type")) %>%
  ggplot(aes(x = neighborhood, y = estimate)) +
  geom_point() +
  facet_wrap(. ~ term) +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust =1))
```

It worked!



